### 2013-06-19 Tex/chapters/results.tex
Einrückung im Quellcode verbessert
Angefangen den Tc_norm Verlauf zu beschreiben

        \subfigure[][]
        {
            \label{sfig:Tc_norm:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
        }
        \caption[Critical Temperature over different disturbance parameters]
                {Top: Critical temperatures over different
                 disturbance parameters for
                 \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
                 \subref{sfig:Tc:GG} the Gabriel Graph.\\
                 Middle: Mean sum of the coupling constants to all
                 neighbors over different disturbance parameters for
                 \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
                 \subref{sfig:sumJ:GG} the Gabriel Graph.\\
                 Bottom: Normalized critical temperatures over different
                 disturbance parameters for
                 \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
                 \subref{sfig:Tc_norm:GG} the Gabriel Graph.
                }
        \label{fig:Tc}
    \end{figure}
    % I don't know what all that means...

>>>>

        \subfigure[][]
        {
            \label{sfig:Tc_norm:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_norm}
        }
        \subfigure[][]
        {
            \label{sfig:Tc_norm:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc_norm}
        }
        \caption[Critical Temperature over different disturbance parameters]
        {
            Top: Critical temperatures over different
            disturbance parameters for
            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc:GG} the Gabriel Graph.\\
            Middle: Mean sum of the coupling constants to all
            neighbors over different disturbance parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Normalized critical temperatures over different
            disturbance parameters for
            \subref{sfig:Tc_norm:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_norm:GG} the Gabriel Graph.
        }
        \label{fig:Tc}
    \end{figure}\\
    % I don't know what all that means...
    The Gabriel graph, which is shown on the right side of fig. \ref{fig:Tc},
    jumps from \(\sigma = 0\) to \(\sigma > 0\). This is easily explained
    by the definition of the Gabriel graph and it's aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:GG_sigma:zero}
            \includegraphics[width=0.45\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][]
        {
            \label{sfig:GG_sigma:notzero}
            \includegraphics[width=0.45\textwidth]{images/GG/sigma_g0}
        }
        \caption[]
        {
            Gabriel graph with periodic boundary conditions for
                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    Moreover fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}
    show monotonically decreasing \(T_c\) with increasing disturbance
    parameter \(\sigma\). The froms of both curves are similar, but the
    one for the Relative Neighborhood graph \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:Tc}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
